Cross-Loop Optimization of Arithmetic Intensity for Finite Element Local Assembly

### 2014-11-03 TACO-paper-v2/coffee.tex
edits back to 25 pages

\begin{bottomstuff}
Author's addresses: Fabio Luporini $\&$ Florian Rathgeber $\&$
Gheorghe-Teodor Bercea $\&$ Paul H. J. Kelly, Department of Computing,
Imperial College London; Ana Lucia Varbanescu, Informatics Institute,
University of Amsterdam; David A. Ham, Department of Computing and
Department of Mathematics, Imperial College London; J. Ramanujam,
Center for Computation and Technology and the School of Elec.~Engr.\&
Comp.~Sci., Louisiana State University.
\end{bottomstuff}

@@

\section*{Acknowledgments}
This research is partly funded by the MAPDES project, by the
Department of Computing at Imperial College London, by EPSRC through
grants EP/I00677X/1, EP/I006761/1, and EP/L000407/1, by NERC grants
NE/K008951/1 and NE/K006789/1, by the U.S.  National Science
Foundation through grants 0811457, 0926687 and 1059417, by the
U.S. Army through contract W911NF-10-1-000, by 
Louisiana State University and by a
HiPEAC collaboration grant. The authors would like to thank Carlo
Bertolli, Lawrence Mitchell and Francis Russell for their invaluable
suggestions and their contribution to the Firedrake project.  We thank
the ACM TACO and HiPEAC'15 reviewers for their suggestions that led to
a significantly improved version.

>>>>

\begin{bottomstuff}
This research is partly funded by the MAPDES project, by the
Department of Computing at Imperial College London, by EPSRC through
grants EP/I00677X/1, EP/I006761/1, and EP/L000407/1, by NERC grants
NE/K008951/1 and NE/K006789/1, by the U.S.  National Science
Foundation through grants 0811457, 0926687 and 1059417, by the
U.S. Army through contract W911NF-10-1-000, by 
Louisiana State University and by a
HiPEAC collaboration grant. The authors would like to thank Carlo
Bertolli, Lawrence Mitchell and Francis Russell for their invaluable
suggestions and their contribution to the Firedrake project.  We thank
the ACM TACO and HiPEAC'15 reviewers for their suggestions that led to
a significantly improved version.

Author's addresses: Fabio Luporini $\&$ Florian Rathgeber $\&$
Gheorghe-Teodor Bercea $\&$ Paul H. J. Kelly, Department of Computing,
Imperial College London; Ana Lucia Varbanescu, Informatics Institute,
University of Amsterdam; David A. Ham, Department of Computing and
Department of Mathematics, Imperial College London; J. Ramanujam,
Center for Computation and Technology and the School of Elec.~Engr.\&
Comp.~Sci., Louisiana State University.
\end{bottomstuff}

@@

\comment{
\section*{Acknowledgments}
This research is partly funded by the MAPDES project, by the
Department of Computing at Imperial College London, by EPSRC through
grants EP/I00677X/1, EP/I006761/1, and EP/L000407/1, by NERC grants
NE/K008951/1 and NE/K006789/1, by the U.S.  National Science
Foundation through grants 0811457, 0926687 and 1059417, by the
U.S. Army through contract W911NF-10-1-000, by 
Louisiana State University and by a
HiPEAC collaboration grant. The authors would like to thank Carlo
Bertolli, Lawrence Mitchell and Francis Russell for their invaluable
suggestions and their contribution to the Firedrake project.  We thank
the ACM TACO and HiPEAC'15 reviewers for their suggestions that led to
a significantly improved version.
}
